TBD

### 2019-09-13 manuscript/manuscript.Rmd
minor edits to impact summary.

The loss of biodiversity is rewiring the web of life; however, we are currently in a poor position to predict how this will affect the ability of populations to evolve and adapt to future environments. To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or only allowed one of the predators to impose selection on a common prey. We found that the loss of predators increased the number of prey traits under selection. This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits. Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments. Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.

>>>>

The loss of biodiversity is rewiring the web of life; however, it is uncertain <!--we are currently in a poor position to predict-->how this will affect the ability of remaining populations to evolve and adapt to future environments. To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or removed all but one of the predators that was able to impose selection on a common prey. We found that the loss of predators increased the number of prey traits under selection, indicating that the trajectory of evolution was more constrained to a specific combination of traits<!--. This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits-->. Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments. Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.
